% !TEX root = ../main.tex

\begin{cnabstract}

    本文介绍了一个用于撰写山东大学博士学位论文的 \LaTeX{} 模板。该模板旨在帮助博士研究生按照学校的
    格式要求，快速、高效地编写和排版学位论文。模板包括了封面、摘要、目录、正文、参考文献等部分的格式
    设置，并提供了详细的使用说明和示例代码。通过使用该模板，用户可以专注于论文内容的撰写，而无需担心
    排版问题，从而提高论文写作的效率和质量。

    本模板是在 sduthesis.cls(\url{https://github.com/Liam0205/sduthesis/}) 这一模板的基
    础上进行修改的，感谢原作者的辛勤劳动。该模板在参考的模板的基础上，修改了部份格式，消除了部份关于
    字体的警告，使之能在我的环境下正常编译。然而，由于本人技术水平有限，模板难免存在一些问题和不足之
    处，还请各位使用者批评指正，共同完善。

    \cnkeywords{山东大学； 博士学位论文； \LaTeX{} 模板}

\end{cnabstract}

\begin{enabstract}

    This document introduces a \LaTeX{} template for writing doctoral dissertations
    at Shandong University. The template is designed to help doctoral students
    write and format their dissertations quickly and efficiently according to the
    school's requirements. The template includes format settings for the cover,
    abstract, table of contents, main text, references, etc., and provides detailed
    instructions and sample code. By using this template, users can focus on
    writing the content of the dissertation without worrying about formatting
    issues, thereby improving the efficiency and quality of dissertation writing.

    This template is based on the sduthesis.cls template
    (\url{https://github.com/Liam0205/sduthesis/}), and I would like to thank the
    original author for his hard work. This template modifies some formats based on
    the referenced template, eliminates some warnings about fonts, and allows it to
    compile normally in my environment. However, due to my limited technical level,
    the template inevitably has some problems and shortcomings. I hope that users
    can criticize and correct them to improve them together.

    \enkeywords{Shandong University; Doctoral Thesis; \LaTeX{} Template}

\end{enabstract}